DRAFT \\ From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2016-08-09 2015CompleteDerivation/completeDerivation.tex
Fix measurement device argument

	Another issue arises if we include the probe in our description. Say $a \in A$ is the state of our system and $b \in B$ the state of our probe, the future state $\hat{a}=f(a)$ because the system is deterministic, but $\hat{b}=g(a,b)$ because the probe needs to be affected by the system. This means $(a, b) \mapsto (\hat{a}, \hat{b})$ is not a reversible map. If we want determinisms and reversibility for the combined system, we either have two isolated systems $\hat{a}=f(a)$ and $\hat{b}=g(b)$, which means the probe can't learn anything about the system, or two interacting systems $\hat{a}=f(a, b)$ and $\hat{b}=g(a, b)$, which means our system is not deterministic as its future state is determined by the state of the probe. In other words: we can't expect to have deterministic and reversible evolution at all levels of aggregation and have the parts interact in any physically meaningful way.

>>>>

	Another issue arises if we include the measuring device in our description. Say $a \in A$ is the state of our system and $b \in B$ the state of our measuring device, the future state $\hat{a}=\hat{a}(a)$ because the system is deterministic, $\hat{b}=\hat{b}(a,b)$ because the measuring device needs to be affected by the system and $a=f(\hat{b})$ because we should be able to know the original state by looking at the measuring device. This means $(a, b) \mapsto (\hat{a}, \hat{b})$ is not a reversible map. We would have $b = b(\hat{a}(f(\hat{b})), \hat{b}) = b(\hat{b})$ and $a=f(\hat{b})$: the whole past state cannot be reconstructed just by looking at the future state of the measuring device. If we want determinisms and reversibility for the combined system, either both systems $\hat{a}=\hat{a}(a, b)$ and $\hat{b}=\hat{b}(a, b)$ are not independently deterministic or the second is not a measuring device $a \neq f(\hat{b})$. In other words: we can't expect to have deterministic and reversible evolution at all levels of aggregation and have the parts interact in any physically meaningful way.
